Progress Report on One Simulated Dataset

### 2023-10-25 Docs/ProgressReportSim.Rmd
update mean function in the debias step

---
title: "Progress Report on One Simulated Dataset"
author: "Ying Jin"
date: "2023-09-15"
output: 
  html_document:
    self_contained: no
    number_sections: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
    font: 12pt
---

@@

```{r, class.source = "fold-show"}
# usethis::edit_r_environ()
t1 <- Sys.time()
debias_glmm <- bam(Y ~ s(t, bs="cr", k=10)+
                     s(id, by=phi1, bs="re")+
                     s(id, by=phi2, bs="re")+
                     s(id, by=phi3, bs="re")+
                     s(id, by=phi4, bs="re"), 
                   family = binomial, data=train_df, 
                   method = "fREML",
                   discrete = TRUE)
t2 <- Sys.time()
t_debias <- t2-t1 # less than 45 seconds
```

@@

This is pretty much a linear functions. Is that supposed to happen?

```{r, class.source = "fold-show"}
new_mu <- predict(debias_glmm, type = "terms")[, 1]
new_mu <- unique(new_mu)
plot(unique(train_df$t), new_mu, type = "l")
```

@@

>>>>

---
title: "Progress Report on One Simulated Dataset"
author: "Ying Jin"
date: "2023-09-15"
output: 
  html_document:
    self_contained: yes
    number_sections: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
    font: 12pt
---

@@

```{r, class.source = "fold-show"}
# usethis::edit_r_environ()
t1 <- Sys.time()
debias_glmm <- bam(Y ~ s(t, bs="cc", k=10)+
                     s(id, by=phi1, bs="re")+
                     s(id, by=phi2, bs="re")+
                     s(id, by=phi3, bs="re")+
                     s(id, by=phi4, bs="re"), 
                   family = binomial, data=train_df, 
                   method = "fREML",
                   discrete = TRUE)
t2 <- Sys.time()
t_debias <- t2-t1 # less than 45 seconds
```

@@

The shape of the function depends very much on how the basis functions are constructed. For example, cubic spline would lead to a linear mean and cyclic cubic spline would lead to the function below. What's a good way to decided?

```{r, class.source = "fold-show"}
new_mu <- predict(debias_glmm, type = "terms")
length(unique(new_mu[,1]))

new_mu <- unique(new_mu[,1])
plot(t, new_mu, type = "l")
```

@@

```{r}
data.frame(
  df_pred$pred0.4[df_pred$t>0.4],
  df_pred3$pred0.4[df_pred3$t>0.4]
)
